---
title: "Using classR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using classR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

This package runs a course on GitHub from R. It does not use GitHub
Classroom. Each student gets a private repo in your organization, your
starter files get pushed in, and the student is added as a collaborator.

# Before you start

You need an organization that already exists. The GitHub API cannot
create one. Please make it once in the browser. You also need `git` on your
system for collecting submissions.

Your roster is a CSV with at least a column named `handle` holding GitHub
usernames.

```
handle
student1
student2
student3
```

# Token

Run `setup_github_token()` once. It opens the token page with the right scopes already selected, checks the token authenticates and carries `repo` and
`admin:org`, then saves it to `~/.Renviron`.

```{r}
library(classR)
setup_github_token()
```

If the token is missing a scope, it tells you which one and saves
nothing.

# Set the organization

Please do this for each session but replace it with your own organization's
name.

```{r}
set_org("ISTA421INFO521")
```

# Assign

Put your starter files in a folder within your working directory. Then, use `assign_homework` to push them to every student's repo. The repo for each student is named `prefix-handle`, so `hw1-student1` and so on.

```{r}
res <- assign_homework("roster.csv", "hw1_files", prefix = "hw1")
res
table(res$status)
```

`res` has one row per student with a `status` of `ok`, `exists`,
`create_error`, or `setup_error`. Rows that already existed are skipped.
You can run this again without trouble.

```{r}
res[res$status %in% c("create_error", "setup_error"), ]
```

By default students get `push` access. Use `permission = "admin"` if you
want students to manage their own repos.

# Check

Confirm every repo is there.

```{r}
status <- check_homework("roster.csv", prefix = "hw1")
status[!status$exists, ]
```

# Update files

Use `update_homework()` you need to fix or add a starter file after assigning, push it again. This function creates files that are missing and overwrites files that exist.

```{r}
update_homework("roster.csv", "hw1_fixes", prefix = "hw1")
```

Note that updating overwrites whatever is at those paths within the repo. If a student already edited a file you push, your version replaces theirs in the latest
commit. The old content stays in history.

# Collect

There's a function that pull everyone's work into a local folder. Submissions land under `dest/prefix/handle`. You can run it as many times as you need.

```{r}
collect_homework("roster.csv", prefix = "hw1", dest = "submissions")
```

# Notes on how it works

Note that files are pushed through the GitHub contents API, one file per call, each as its own commit. This is fine for small starter folders. For large or
deeply nested projects it is slow and noisy in the history...

Collecting uses git, not the API, since it moves whole repositories.

Adding a collaborator sends an invitation. Students accept it from their
GitHub email or notifications before they can push.
